### 2014-03-13 src/introduction.Rnw
udpate

% 1. Describe the problem
% 2. State your contributions
Mutation analysis is a method of evaluation of quality of test-suites. It
involves producing a family of mutants with simple differences from the
original program, and evaluating the effectiveness of test-suites against
these mutants~\cite{lipton1971fault, ammann2008introduction}.  Previous
research~\cite{andrews2005mutation} suggests that mutations thus introduced
behave in a fashion similar to the real-faults with respect to the difficulty
of detection.

@@

A major strain of research into cost-reduction of mutation
analysis is to choose a smaller representative set of
mutants~\cite{offutt2001mutation,jia2011analysis}-- often called the ``do
fewer'' approach. This approach can be generally divided into selective
strategies and sampling strategies.

@@

However, as pointed out by Zhang et al.~\cite{zhang2013ase}, the
field has a serious lacuna in large scale research, both in the
size of the programs studied, and in the number and diversity of
programs, which reduces our confidence in their results. This is
true for selective mutation studies, studies in sampling, and also
for comparatively newer studies that attempt to combine them. This is
particularly worrisome if mutation analysis is to gain wider acceptance
among testing professionals. Further, quite a few of the influential
studies~\cite{offutt1993experimental,offutt1996anexperimental,wong1995reducing,mresa1999efficiency}
has been conducted on older programming languages such as Fortran with
operators specific to it, and are not directly applicable to newer languages
such as Java, with significant differences. Finally, with the modern research
into the ``do-smarter'' approach using byte code based mutation -- eliminating
the compilation step -- operators based on source code modification is no
longer be applicable, and their equivalents in the bytecode needs to be
found and compared with other approaches. A detailed discussion of these
issues can be found in Section~\ref{sec:related}.

% RAHUL>AMIN: I find the non-bulleted contributions better flowing as I can work the references
% to other sections into it. Let me know if you have a better idea (As it stands neither my
% previous wording, nor your bulleted list reads good)
We have attempted to rectify this situation with a large scale study
of industrial programs.  As detailed in Section~\ref{sec:methodology},
we sample 188 real world Java programs from Github, with size ranging
from 50loc to 100kloc, which allows us to make widely applicable
statistical inferences. We provide the results from running both original human
generated test-suites, and also programmatically generated test-suites,
increasing the applicability of our findings to both researchers who seek to
compare test-suites quickly, and to industrial software testers who might be
looking for a way to reduce the time of their build cycle when using mutation
coverage. The Section~\ref{sec:methodology} discusses the sampling strategies
attempted, and the operator selection strategies in detail, and the results of
our experiment are given in Section~\ref{sec:results}, followed by detailed
discussion of what it implies in section ~\ref{sec:discussion}. The research
concludes in Section~\ref{sec:conclusion}.

@@

\begin{itemize}
\item Our study is the largest so far in terms of both the size of programs
involved (50loc to 100kloc), and the number of programs analyzed
(188 unique open source projects) for mutant reduction strategies. This allows
for stronger and widely applicable statistical inferences to be drawn.
\item We compare a much large number of mutant reduction strategies, especially
with respect to their predictive power over the final mutation score, the
expected mutant reduction, and the stability of the amount of mutant reduction
expected. Our sampling strategies include some that were suggested by other
researchers, and also a few novel strategies that has not been published elsewhere.
\item Our recommendations are valid for both testing researchers who might be
comparing programmatically generated test-suites, and software testing
professionals working on real test-suites.
\item Most importanly, we find that the simplest strategy of mutation reduction,
that of x\% sampling is better than more sophesticated strategies in predicting
the final mutation score. This is true not only for those strategies that we
analyzed but also for any other strategies that seek to predict the full mutation
score by looking at only a subset of mutants, irrespective of the kind of
reduction used (operator selection, sampling or clustering, or any other).
\end{itemize}

>>>>

% 1. Describe the problem
% 2. State your contributions
Mutation analysis is a method of evaluating the quality of test-suites. It
involves producing a family of mutants with simple differences from the
original program, and evaluating the effectiveness of test-suites against
these mutants~\cite{lipton1971fault, ammann2008introduction}.  Previous
research~\cite{andrews2005mutation} suggests that mutations thus introduced
behave in a fashion similar to the real-faults with respect to the difficulty
of detection.

@@

A major strain of research into cost-reduction of mutation
analysis is to choose a smaller representative set of
mutants~\cite{offutt2001mutation,jia2011analysis}-- often called the \textit{do
fewer} approach. This approach can be generally divided into selective
strategies and sampling strategies.

@@

However, as pointed out by Zhang et al.~\cite{zhang2013ase}, the
field has a serious lacuna in large scale research, both in the
size of the programs studied, and in the number and diversity of
programs, which reduces our confidence in their results. This is
true for selective mutation studies, studies in sampling, and also
for comparatively newer studies that attempt to combine them. This
is particularly worrisome if mutation analysis is to gain wider
acceptance among testing professionals. Further, quite a few of the influential
studies~\cite{offutt1993experimental,offutt1996anexperimental,wong1995reducing,mresa1999efficiency}
has been conducted on older programming languages such as Fortran with
operators specific to it, and are not directly applicable to newer
languages such as Java, with significant differences. Finally, with the
modern research into the byte code based mutation (a \textit{do smarter}
approach for eliminating the compilation step, and gaining execution speed)
operators based on source code modification is no longer be applicable,
and their equivalents in the bytecode needs to be found and compared with
other approaches. A detailed discussion of these issues can be found in
Section~\ref{sec:related}.

We have attempted to rectify this situation with a large scale study of
industrial programs.  As detailed in Section~\ref{sec:methodology}, we sample
188 real world Java programs from Github, with size ranging from 50loc to
100kloc, which allows widely applicable statistical inferences to be made. We
provide the results from running both original human generated test-suites, and
also programmatically generated test-suites, increasing the applicability of
our findings to both researchers who seek to compare test-suites quickly,
and to industrial software testers who might be looking for a way to
reduce the time of their build cycle when using mutation coverage. The
Section~\ref{sec:methodology} discusses the sampling strategies attempted,
and the operator selection strategies in detail, and the results of our
experiment are given in Section~\ref{sec:results}, followed by detailed
discussion of what it implies in section ~\ref{sec:discussion}. The research
concludes in Section~\ref{sec:conclusion}.

@@

\begin{itemize}

\item Our study is the largest so far in terms of both the size of programs
involved (50loc to 100kloc), and the number of programs analyzed (188
unique open source projects) for mutant reduction strategies. This allows
for stronger and widely applicable statistical inferences to be drawn.

\item We compare a much large number of mutant reduction strategies,
especially with respect to their predictive power over the final mutation
score, the expected mutant reduction, and the stability of the amount of
mutant reduction expected. Our sampling strategies include some that were
suggested by other researchers, and also a few novel strategies that has
not been published elsewhere.

\item Our recommendations are valid for both testing researchers who might
be comparing programmatically generated test-suites, and software testing
professionals working on real test-suites.

\item Most importantly, we find that random sampling strategies perform
better than operator selection strategies consistently in predicting the
final mutation score.

\end{itemize}

### 2014-03-13 src/related.Rnw
.
udpate

\section{Related Work}
\label{sec:related}
In this section we summarize the related work. There have been
different approaches to reduce the cost of mutation analysis.
Jia and Harman \cite{jia2011analysis} have categorized them into two
broad categories: Mutation Reduction and Execution Reduction.

\subsection{Mutant Reduction}
The idea of using a subset of mutants instead of all of them started
by Mathur\cite{mathur1991performance} and 
further have developed by Wong et al.\cite{wong1993mutation, wong1995reducing}
 and Offut et al. \cite{offutt1993experimental}.
Each of them targeted the mutation operators of Mothra \cite{Mothra}.
Mathur \cite{mathur1991performance} suggested removal of two mutation operators
has little effect on the effectiveness of mutation testing.
Offut et al. \cite{offutt1993experimental} experiment removal of 
upto six mutation operators. They observe that the reduction has
little effect on the mutation score.
Wong and Mathur \cite{wong1995reducing} suggested two operators in Mothra system
that could approximate mutation score.

Some studies have tried to find set of \emph{sufficient mutation operators} --minimal set
of operators that while reducing the cost of mutations, its mutation score maintains
a good correlation with mutaion score of the original set of operators.
Barbosa et. al.\cite{barbosa2001toward} provides a set of guidelines for selecting 
such mutation operators. Namin et al.\cite{namin2006finding,siami2008sufficient} 
formulate this problem as a variable reduction problem, and apply statistical 
approaches. They found a subset of 28 operators out of 108 opertors as the sufificient operators.
Recently, Deng et al~\cite{deng2013empirical} considers the effect of using a single mutation operator 
-- the statement deletion operator. They define deletion for different language elements,

Wong and Mathur \cite{wong1995reducing}, Acree\cite{Acree1980}, and Budd\cite{Budd1980}  suggest \%x sampling of all mutants.
They observed that random sampling of mutatnts can greatelly reduces the cost of mutation analysis while
it can closely approximate the mutation score. Recently, Zhang et al. \cite{zhang2013ase} has shown that sampling
as small as five percent is a good preditor of mutation score.

@@

Zhang et al.\cite{zhang2010operator} compare operator based mutant selection in 
\cite{barbosa2001toward,siami2008sufficient,offutt1996anexperimental} to random mutant selection. 
%They compare three diffrent operator based selection techniques from Offutt et al., Barbosa et al., and Namin 
%et al. against random mutant selection, with equal mutant probability, and equal mutagen probaiblity. 
They find that none of these selection techniques are superior to random selection, with same number of 
mutants. They also find that equal mutation sampling is more effective for larger subjects compared to 
equal mutagen sampling and the reverse is true for smaller subjects.
Zhang et al.\cite{zhang2013ase} investigates 8 sampling strategies on top of operator
based mutant selection. They find that sampling strategies based on program componenets.
(based on methods) performed best.

This work is closely related to Zhang et al.\cite{zhang2013ase}. We extend the scope of 
their study with much wider range of mutation selection and we experimented them on much more
real-world projects.

@@

\subsection{Execution Reduction}

Weak mutation, devised by Howden \cite{howden1982weak}, considers a mutant as detected, if 
the states of program after the mutated statement in mutant and the original
program differ. Several oher studies have refined the idea theoretically \cite{horgan1990weak}and
observed its effectiveness emperically\cite{offutt1994empirical,Offutt:1991:SWM:120807.120826}.

Some studies have utlized parallel computation to enhance the execution time of 
the mutation testing \cite{}. Others have used custom built compilers and interpretors \cite{}
to reduce the overall compile time in mutation testing \cite{}.

>>>>

\section{Related Work}
\label{sec:related}
In this section we summarize the related work. There have been
different approaches to reduce the cost of mutation analysis.
These were categorized by Offutt and Untch~\cite{offutt2001mutation}
into three approaches: Do \textit{fewer}, \textit{smarter}, \textit{faster}.
The fewer approaches includes selective mutation and mutant sampling while
weak mutation, parallelization of mutation analysis, space time trade offs
are grouped under the umbrella of \textit{do smarter}. Finally
\textit{do faster} approaches include byte code based mutation analysis
systems like PIT, and similar binary patching methods.

The idea of using a subset of mutants was born along with the mutation analysis
itself. Budd~\cite{budd1980mutation} and Acree~\cite{Acree1980} showed that
even 10\% sampling can achieve 99\% accuracy for the final score.

It was further investigated by Mathur~\cite{mathur1991performance},
Wong et al.~\cite{wong1993mutation,wong1995reducing}, and
Offutt et al.~\cite{offutt1993experimental} using the Mothra~\cite{Mothra}
mutation operators for Fortran. Mathur~\cite{mathur1991performance,wong1995reducing}
suggested constrained mutation where in only two mutation operators were used which
were felt to be better than using the entire set.

% Operator Selection also assumes that fault detection ability of some operators
% are higher than others, and hence some operators should have higher weight
% than others. ~\cite{wong1997comparison}

A number of studies in the past have looked at the relative merits of operator
selection and random sampling criteria, starting with Wong and Mathur in
1995~\cite{wong1995reducing}. They compared x\% selection of each mutant type
with operator selection of just two mutation operators, and finds that both
achieved similar accuracy and reduction (80\%). This study was conducted on
five small programs in C and Fortran.

Some studies have tried to find set of \emph{sufficient mutation operators} that
while reducing the cost of mutations, maintains the correlation with the full
mutation score. Offutt~\cite{offutt1993experimental} suggested n-selective
approach which advocates step by step removal of mutation operators that produced
the largest number of mutants.

Mresa et al.\cite{mresa1999efficiency} used the cost of detection of mutants as
a means of selection, and uses it to define a set of operators. They find
that if very high mutation score close to 100\% is required, x\% selective
mutation is better than operator selection, and conversely for less stringent
scores, operator selection would be better if cost of mutant is considered.

Barbosa et. al.\cite{barbosa2001toward} provides a set of guidelines for selecting
such mutation operators. Namin et al.\cite{namin2006finding,siami2008sufficient}
formulate this problem as a variable reduction problem, and apply statistical
approaches. They found a subset of 28 operators out of 108 operators as the sufficient
operators.

Using only the statement deletion operator was first suggested by
Untch~\cite{untch2009onreduced}, who found that it correlated ($R^2 = 0.97$) with the
full mutation score better than other operator selection methods, while generating the
least number of mutants.  This was further reinforced by Deng et al.~\cite{deng2013empirical}
who defined deletion for different language elements, and found that an accuracy of 92\% is
achieved while reducing the mutants by 80\%.

Zhang et al.~\cite{zhang2010operator} compares operators based mutant selection in
~\cite{barbosa2001toward,siami2008sufficient,offutt1996anexperimental} to random mutant selection.
They find that none of these selection techniques are superior to random selection, with same number of
mutants. They also find that equal mutation sampling is more effective for larger subjects compared to
equal mutagen sampling and the reverse is true for smaller subjects.

Recently, Zhang et al.~\cite{zhang2013ase} confirmed that sampling as few as 5\% mutants
was sufficient for a very correlation (99\%) with the full mutation score, while sampling even
fewer mutants has good potential for retaining high accuracy. They investigate 8 sampling
strategies on top of operator based mutant selection and find that sampling strategies
based on program components (based on methods) performed best.

@@

This work is closely related to Zhang et al.~\cite{zhang2013ase}. We extend the scope of
their study with much wider range of mutation selection and we experimented them on much more
real-world projects.

@@

%\subsection{Execution Reduction}

%Weak mutation, devised by Howden \cite{howden1982weak}, considers a mutant as detected, if
%the states of program after the mutated statement in mutant and the original
%program differ. Several oher studies have refined the idea theoretically \cite{horgan1990weak}and
%observed its effectiveness emperically\cite{offutt1994empirical,Offutt:1991:SWM:120807.120826}.

%Some studies have utlized parallel computation to enhance the execution time of
%the mutation testing \cite{}. Others have used custom built compilers and interpretors \cite{}
%to reduce the overall compile time in mutation testing \cite{}.
